---
title: "FARS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

datfolder <- system.file("extdata", package = "courseraFARS")
file.copy(
  file.path(datfolder, dir(datfolder)),
  file.path(getwd(), dir(datfolder))
)
```

## *Read, summarise and visualize Fatality Analysis Reporting System data*
This package comes with a limited number of very basic functions. To demonstrate the use of these, the package comes with raw csv files which can be accessed with the following command:
```{r}
datfolder <- system.file("extdata", package = "courseraFARS")
dir(datfolder)
```

```{r}
library(courseraFARS)
```

1. `fars_read` loads the csv data into a `tibble::tbl_df`

```{r}
(x <- fars_read(dir(datfolder)[1]))
```


2. `fars_read_years` loads multiple csv files into a list of tibbles with only the `MONTH` and `year` columns.

```{r}
(x <- fars_read_years(2013:2015))
```

3. `fars_summaize_years` returns tibble with counts for each month in the specified years
```{r}
(x <- fars_summarize_years(2013:2015))
```


4. `fars_map_state` can be used for plotting the geographical coordinates of fatal injuries within a year for the specified state. 

```{r fig.align='center', fig.height=4, fig.width=5}
fars_map_state(1, 2013)
```


```{r deletefiles, include=FALSE}
file.remove(dir(datfolder))
rm(datfolder)
```



